---
title: "multi database"
author: "Steph"
date: "5/5/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(parallel)
library(profvis)
library(data.table)
library(prodlim)
library(dplyr)
library(sqldf)
library(DBI)
library(RSQLite)
library(readxl)
library(pbmcapply)
library(gtools)
```

```{r}
source("Functions/chpt5 - multi database/licenseplates.R") ## less than 125000
source("Functions/chpt5 - multi database/creditcard.R")  # less than 5^5
source("Functions/chpt5 - multi database/IMEI.R") ## less than 5^5
source("Functions/chpt5 - multi database/multidna.R") ## less than 10^6
```

SCENARIO 1:: (i.e we have a hypothesis)
we have a DNA sample, and their ID, but we need more evidence. 
how much evidence does this give us against the culprit found from the dna evidence?
is this person in the other databases? they dont need to be in all of them







SCENARIO 2:: (no hypothesis, just trawling)
What if we dont have DNA sample, but we have a couple found at the crime scene. How many collisions are there within the guilty databases??

```{r}

N <- 1000
r <- 6
s <- 10
ndegrade <- 3
nmatch <- 6

p <- 0.27 # plate 
q <- 0.08  # credit 
m <- 0.38 # phone


  
plate <- licenseplates(N)
guiltyplate <- sample_n(plate, N*p)
credit <- creditcard(N)
guiltycredit <- sample_n(credit, N*q)
IMEIdB <- IMEI(N)
guiltyphone <- sample_n(IMEIdB, N*m)
dna <- multidna(N, r, s, ndegrade, nmatch)
colnames(dna) <- c("ID", "csID", "Matches")

guiltyplates <- vector(length = nrow(dna))
guiltycredits <- vector(length = nrow(dna))
guiltyphones <- vector(length = nrow(dna))

for(i in 1:nrow(dna)){
guiltyplates[i] <- ifelse(dna[i,1] %in% guiltyplate[,1], "Yes", "No")
guiltycredits[i] <- ifelse(dna[i,1] %in% guiltycredit[,1], "Yes", "No")
guiltyphones[i] <- ifelse(dna[i,1] %in% guiltyphone[,1], "Yes", "No")


}

data.frame("ID" = dna[,1], "csID" = dna[,2], "License" = guiltyplates, "Phone" = guiltyphones, "Credit" = guiltycredits)
```





