---
title: "Balding2(N,p,r)"
author: "Steph"
date: "5/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(parallel)
library(profvis)
library(data.table)
library(prodlim)
library(dplyr)
library(sqldf)
library(DBI)
library(RSQLite)
library(readxl)
library(pbmcapply)
```

```{r}
source("Functions/nsmatch.R")
```

```{r, doSims}
nsim <- 10^5
tmp <- vector("list", nsim)
n_core <- 14
N <- 10^6
p <- 0.1
m <- 10
r <- 6
s <- 10

s.time <- system.time({
  result <- unlist(pbmclapply(tmp, FUN = function(y) { 
                             nsmatch(N, p, m, r, s) },
                                  mc.cores = n_core)) 
  
})
YesSim <- sum(result)
YesSim/length(result)
s.time

closeAllConnections()
```


# # # # # SIMULATION 2 ::: P(O|G^c) # # # # # 

### BALDING2A RESULTS### 
N = 1e+07, p = 0.1 ( m = 1)
n_sim = 10,      YesSim/n_sim = 0.3      time elapsed = 123.204  user time = 546.953
n_sim = 100,     YesSim/n_sim = 0.44     time elapsed = 1045.189 user time = 6931.444
n_sim = 1000,    YesSim/n_sim = 0.378    time elapsed = 9694.802 user time = 72409.594
n_sim = 10000,   YesSim/n_sim = 0.369    time elapsed = 96110.36  user time = 727237.69
n_sim = 100000,  YesSim/n_sim = 0.3669   time elapsed = 1294371  user time = 9635277

### BALDING2B RESULTS### 
N = 1e+07, p = 0.1, m = 10 
n_sim = 10,     # results = 100      YesSim/n_sim = 0.31      time elapsed = 2139.586 user time = 8337.929
n_sim = 100,    # results = 1000     YesSim/n_sim = 0.361     time elapsed = 16903.44 user time = 102081.72
n_sim = 1000,   # results = 10000    YesSim/n_sim = 0.3632    time elapsed = 160569.8 user time = 1018957.4
n_sim = 10000,  # results = 100000   YesSim/n_sim =     time elapsed =  user time = 
n_sim = 100000, # results = 1000000  YesSim/n_sim =     time elapsed =  user time = 

### BALDING2B RESULTS### 
N = 1e+06, p = 0.1, m = 10 
n_sim = 10,     # results = 100      YesSim/n_sim =  0.53    time elapsed =  user time = 
n_sim = 100,    # results = 1000     YesSim/n_sim =  0.529    time elapsed =  user time = 
n_sim = 1000,   # results = 10000    YesSim/n_sim =  0.5433   time elapsed =  user time = 
n_sim = 10000,  # results = 100000   YesSim/n_sim =  0.53858    time elapsed =  user time = 
n_sim = 100000, # results = 1000000  YesSim/n_sim =  0.537462    time elapsed =  user time = 



