---
title: "Balding(N,p,r)"
author: "Steph"
date: "5/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(parallel)
library(profvis)
library(data.table)
library(prodlim)
library(dplyr)
library(sqldf)
library(DBI)
library(RSQLite)
library(readxl)
library(pbmcapply)
```


```{r}
source("Functions/smatch.R")
```


```{r, doSims}
n_sim <- 10^5
tmp <- vector("list", n_sim)
n_core <- 2
N <- 10^6
p <- 0.1
m <- 10
r <- 6
s <- 10

s.time <- system.time({
  result <- unlist(pbmclapply(tmp, FUN = function(y) { 
                             smatch(N, p, m, r, s) },
                                  mc.cores = n_core)) 
  
})
YesSim <- sum(result == 1)
YesSim/length(result) ## just incase not all sims run, but if they do then length(results) = m * n_sim
s.time

closeAllConnections()
```



# # # # # SIMULATION 1 ::: P(O|G) # # # # # 

### BALDING1A RESULTS### 
N = 1e+07, p = 0.1  (m = 1)
n_sim = 10,      YesSim/n_sim = 0.5
n_sim = 100,     YesSim/n_sim = 0.41     time elapsed = 229.511  user time = 2363.408
n_sim = 1000,    YesSim/n_sim = 0.337    time elapsed = 2200.891 user time = 25261.989
n_sim = 10000,   YesSim/n_sim = 0.36     time elapsed = 21255.34 user time = 257439.10
n_sim = 100000,  YesSim/n_sim = 0.36824  time elapsed = 203119.4 user time = 2501950.4


### BALDING1B RESULTS### 
N = 1e+07, p = 0.1, m = 10 
n_sim = 10,     # results = 100      YesSim/n_sim = 0.36     time elapsed = 211.042  user time = 1216.846
n_sim = 100,    # results = 1000     YesSim/n_sim = 0.397    time elapsed = 1604.808 user time = 14306.665
n_sim = 1000,   # results = 10000    YesSim/n_sim = 0.3648   time elapsed = 14638.63 user time = 143110.56
n_sim = 10000,  # results = 100000   YesSim/n_sim = 0.36833  time elapsed = 1384442.0 user time = 1384442.0 
n_sim = 100000, # results = 1000000  YesSim/n_sim = 0.368654


### BALDING1 RESULTS### 
N = 1e+06, p = 0.1, m = 10 
n_sim = 10,     # results = 100      YesSim/n_sim = 0.92
n_sim = 100,    # results = 1000     YesSim/n_sim = 0.888
n_sim = 1000,   # results = 10000    YesSim/n_sim = 0.9059
n_sim = 10000,  # results = 100000   YesSim/n_sim = 0.90498
n_sim = 100000, # results = 1000000  YesSim/n_sim = 0.904729

