---
title: "BALDING96_3"
author: "Steph"
date: "4/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(parallel)
library(profvis)
library(data.table)
library(prodlim)
library(dplyr)
library(sqldf)
library(DBI)
library(RSQLite)
library(readxl)
library(pbmcapply)
```


```{r}
source("Functions/snsmatch.R")
```

```{r, doSims}
nsim <- 10^5

tmp <- vector("list", nsim)
n_core <- 14

N <- 10^6
p <- 0.1
m <- 10
r <- 6
s <- 10

s.time <- system.time({
  result <- unlist(pbmclapply(tmp, FUN = function(y) { 
                             snsmatch(N, p, m, r, s) },
                                  mc.cores = n_core)) 
  
})
YesSim <- sum(result)
YesSim/length(result)
length(result)/YesSim
s.time

closeAllConnections()
```


### BALDING3 RESULTS### 

N = 1e+07, p = 0.1, m = 10 
## i think if we ran this with a smaller pop it would give a more definitive result

n_sim = 10,     # results = 100      YesSim/n_sim = 1      time elapsed = 12104.982  user time = 4.283
n_sim = 100,    # results = 1000     YesSim/n_sim = 1     time elapsed = user time = 
n_sim = 1000,   # results = 10000    YesSim/n_sim = 0.9997   time elapsed = 82482.572 user time = 19.927
n_sim = 10000,  # results = 100000   YesSim/n_sim =     time elapsed =  user time = 
n_sim = 100000, # results = 1000000  YesSim/n_sim =     time elapsed =  user time = 


N = 1e+06, p = 0.1, m = 10, r = 6, s = 10
n_sim = 10,     # results = 100      YesSim/n_sim = 0.54   Inverse = 1.85185   
n_sim = 100,    # results = 1000     YesSim/n_sim = 0.61  Inverse =  1.639344   
n_sim = 1000,   # results = 10000    YesSim/n_sim = 0.5916 Inverse =  1.690331 
n_sim = 10000,  # results = 100000   YesSim/n_sim = 0.59609 Inverse =   1.677599   
n_sim = 100000, # results = 1000000  YesSim/n_sim = 0.593714 Inverse =   1.684313